---
title: "Fancy Presentation"
author: "Peter E"
date: "May 1, 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## New Slide
Some content

***
Some content but without title. Sometimes useful

## Main Title
### First level subheading
#### Second level subheading

## Bullets and Lists
- Bullet one
- Bullet two

1. Ordered list 1
2. Ordered list 2

* Another way to do a bullet

## Text Formatting

*Italicized text*

**Bold text**

`Code chunk in line`

```{r echo=TRUE}
print('R code chunk')

```


## Show Data and plots 1
```{r, comment = ""}
head(mtcars)

```

## Show Plots
```{r, fig.cap='Relationship of Car Weight to MPG'}
plot(mpg~wt,data=mtcars,col=cyl,xlab='Weight',ylab='MPG',pch=19)
mdl<-lm(mpg~wt,data=mtcars)
abline(mdl,col='blue')
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

